---
title: "BC Climate: Monthly summary and long term trends"
author:
 name: "Aseem Sharma e-mail: aseem.sharma@gov.bc.ca"
 corresponding: true
 email: Aseem.Sharma@gov.bc.ca
 affiliations:
    id: "FFEC"
    name: "Future Forest Ecosystems Centre, FCCSB, OCF, BC Ministry of Forests" 
date: "`r paste('Date:', format(Sys.time(), '%d %B, %Y'))`"
code-annotations: false
execute:
  echo: false
  warning: false
  output: false
cap-location: bottom
editor: visual
wrap: auto
format: 
 html:
  fig-format: png
  toc_float: true
  toc-location: left
  toc: true
  toc-depth: 6
  toc-title: "Contents"
  number-sections: true
  number-depth: 5
  embed-resources: true
  self-contained: true
 # pdf:
 #  lof: true
 #  lot: false
 #  number-sections: false
 #  fig-pos: 'H'
 #  fig-format: png
 #  fig-dpi: 150
 #  pdf-engine: latexmk
 #  pdf-engine-opt: -xelatex
editor_options: 
 chunk_output_type: console
---

```{=html}
<!-- 
below modfies the quarto to create print to pdf button and change HTML document to print friendly by changing the format.
-->
```

::: print-button-container
<button id="printButton" class="print-button">

Print to PDF

</button>
:::

```{=html}
<style>
/* General styles for the browser view (from Quarto theme) are untouched */

.print-button-container {
  margin-top: 20px;
  text-align: right;
}

.print-button {
  background-color: #007bff;
  color: white;
  border: none;
  padding: 10px 15px;
  font-size: 14px;
  border-radius: 5px;
  cursor: pointer;
}

.print-button:hover {
  background-color: #0056b3;
}

/* Print-specific styles (only active when .print-mode is applied) */
.print-mode body {
  background-color: white;
  color: black;
  font-size: 12pt;
}

.print-mode .print-button-container {
  display: none; /* Hide the print button during printing */
}

.print-mode h1, .print-mode h2, .print-mode h3 {
  page-break-after: avoid;
}

.print-mode p {
  margin: 1em 0;
}

.print-mode table {
  width: 100%;
  border-collapse: collapse;
}

.print-mode th, .print-mode td {
  border: 1px solid #000;
  padding: 5px;
}

@page {
  size: auto;
  margin: 1in;
  @bottom-center {
    content: "Page " counter(page) " of " counter(pages);
    font-size: 10pt;
    color: #666;
  }
}

@media print {
  body {
    counter-reset: page;
  }

  .print-button-container {
    display: none !important;
  }

  /* Optional: Add page number footer manually for compatibility */
  footer::after {
    content: "Page " counter(page);
    display: block;
    text-align: center;
    font-size: 10pt;
    color: #555;
    margin-top: 2em;
  }
}
</style>
```

```{=html}
<script>
document.getElementById("printButton").addEventListener("click", function () {
  // Add the print-specific class to the <html> element
  document.documentElement.classList.add("print-mode");

  // Trigger the print dialog
  window.print();

  // Remove the print-specific class after a brief delay
  setTimeout(function () {
    document.documentElement.classList.remove("print-mode");
  }, 1000);
});
</script>
```

```{r required}
#| include: false
#| results: hold
#| cache: false

# Required -------------------------------
rqr_pkgs <-
  c(
    'terra',
    "tidyverse",
    'lubridate',
    'zoo',
    'magrittr',
    "Kendall",
    "zyp",
    "tidyterra",
    "colorspace",
    "cptcity",
    "quarto",
    'patchwork',
    'kableExtra'
  )
# Install packages if not
installed_rqr_pkgs <- rqr_pkgs %in% rownames(installed.packages())
if (any(installed_rqr_pkgs == FALSE)) {
  install.packages(rqr_pkgs[!installed_rqr_pkgs])
}
# Load:
lapply(rqr_pkgs , require, character.only = TRUE)

# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

```{r paths}
#| include: false
#| results: 'hold'
#| cache: false
# Paths and results files  ------------------------
# setwd(getwd())
result_plts_pth <- './result_plots/'

# Result files

result_fls <- list.files(path = result_plts_pth,full.names = TRUE )

result_fls_pth <- tibble(result_pth = result_fls)
result_fls_pth

result_pngs <- result_fls_pth %>%
  filter(str_ends(result_pth, ".png"))

# Step 3: Extract plot_type from filename (remove folder and extension)
plot_paths_df <- result_pngs %>%
  mutate(
    file_name = basename(result_pth),
    plot_type = str_remove(file_name, "_\\d{4}_\\d{4}\\.png$"),  # remove "_1950_2025.png"
    plot_type = str_remove(plot_type, "_\\d{4}\\.png$"),         # remove "_2025.png"
    plot_type = str_remove(plot_type, "\\.png$")                 # fallback for non-dated pngs
  ) %>%
  select(plot_type, path = result_pth)

# Optional: Sort or preview
plot_paths_df <- arrange(plot_paths_df, plot_type)
print(plot_paths_df)
write_csv(plot_paths_df , paste0(result_plts_pth,'plots_paths_png.csv' )) # To read later to create png image path

```

```{r plots paths}
#| label: load_plot_paths
#| echo: false
#| cache: true

# Read all plot paths from CSV
plot_paths_df <- read.csv(paste0(result_plts_pth,'plots_paths_png.csv' ), stringsAsFactors = FALSE)
knitr::kable(plot_paths_df)
```

```{r datafiles requirements }
#| include: false
#| cache: false

# Update month
# read following values from render .r file
min_year <- 1951
max_year <- 2025

update_month <- "June"
update_year <- "2025"

years <- seq(min_year, max_year, 1)
years
length(years)
curr_mon_yr <- as.Date(paste0(update_year,update_month,"15"),format = "%Y%B%d" )
curr_mon_yr
prvs12_mon_yr <- curr_mon_yr-365
prvs12_mon_yr
prvs12_mon_yr_1 <- prvs12_mon_yr-30

# prvs_12_mns <- seq.Date((curr_mon_yr-366),curr_mon_yr, by = "month")[2:13]
prvs_12_mns <- rev(seq(as.Date(curr_mon_yr), by="-1 month", length.out = 12))

cur_mon_nam <- format(as.Date(curr_mon_yr), "%B %Y")
cur_yr_nam <- format(as.Date(curr_mon_yr), "%Y")
cur_mon_only <- format(as.Date(curr_mon_yr), "%B")
prv_mon_nam <- format(as.Date(prvs12_mon_yr_1), "%B %Y")
 
# Credit  -----
plt_wtrmrk <-
  "Created by Aseem Sharma (aseem.sharma@gov.bc.ca), BC Ministry of Forests. Data credit: ERA5land/C3S/ECMWF."
plt_wtrmrk
```

```{=html}
<!--
 Climate summary of year `r format(as.Date(curr_mon_yr), "%Y")`

-   annual average temperature was above normal by 2.15°C (spatial range: 0.42°C - 3.63°C).
-   precipitation was less then normal ( upto -36%, average -18%) for most of BC except part of north-western region.
-   While temperature related parameters ( mean, minimum, maximum temperature and VPD) exhibit higher then normal values, moisture related parameters (RH, soil moisture) were below normal for most of the province.
-->
```

## `r format(as.Date(curr_mon_yr), "%B-%Y")` climate summary

```{r cur_mon sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_sum_tab <- result_fls_pth %>%
  filter(str_detect(result_pth , paste0(update_month, '_', update_year, '_bc_climate_summary\\.csv$'))) 
clm_sum_tab

clm_sum_tab_ff <- read_csv(clm_sum_tab$result_pth)
clm_sum_tab_ff
```

```{r cur_mon sumamry table}
#| include: true
#| output: true
#| cache: false
#| label: tbl-mon_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of ", update_month, "-", update_year, 
#|                      ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", update_year, ".")

kbl(clm_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

Below you find the spatial anomalies and long term trend of air temperature, vapor pressure deficit (VPD), total monthly precipitation, relative humidity (RH), and volumetric soil moisture (0 - 1m depth) for the month of `r format(as.Date(curr_mon_yr), "%B-%Y")`.

## Mean temperature and vapor pressure deficit (VPD)

### Anomaly: `r format(as.Date(curr_mon_yr), "%B-%Y")`

```{r fig_tmean_vpd_ano_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-tmean_vpd_ano
#| fig-cap: !expr paste("Anomalies in mean temperature and VPD for ", cur_mon_nam, " relative to climate average of ", cur_mon_only, " (1981–2010).")

# Extract the desired path from plot_paths_df
tmean_vpd_ano_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_tmean_vpd_anomalies")) %>%
  pull(path)

knitr::include_graphics(tmean_vpd_ano_path)
```

### Last 12 months anomaly: `r prv_mon_nam` to `r cur_mon_nam`

```{r fig_tmean_vpd_ano_path12}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-tmean_vpd_ano12
#| fig-cap: !expr paste("Average anomalies in mean temperature and VPD  for ",prv_mon_nam, "to", cur_mon_nam," relative to climate average of 1981 - 2010 .")

tmean_vpd_ano_path12 <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_tmean_vpd_last12months_anomalies")) %>%
  pull(path)

knitr::include_graphics(tmean_vpd_ano_path12)
```

### Long term trends

#### Spatial trends: `r format(as.Date(curr_mon_yr), "%B")` 1950 - `r update_year`

```{r fig_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of mean temperature and VPD anomalies for", cur_mon_nam ,":1950 - ",cur_yr_nam, ".The black dots indicate grid cells with statistically signficnat trends. Anomalies are calcuated relative to 1981-2010 climatology")

tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_tmean_vpd_longterm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(tmean_vpd_sptrn_path)
```

#### Time series trends: `r format(as.Date(curr_mon_yr), "%B")` 1950 - `r update_year`

```{r fig_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for", cur_mon_nam ,":1950 - ",cur_yr_nam, ". Anomalies are calcuated relative to 1981-2010 climatology")

tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(tmean_vpd_tstrn_path)
```

## Precipitation, Relative Humidity (RH) and soil moisture


### Anomaly: `r format(as.Date(curr_mon_yr), "%B-%Y")`

```{r fig_prcp_rh_sm_ano_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-prcp_rh_sm_ano
#| fig-cap: !expr paste("Anomalies in total precipitation, relative humidity and volumetric soil mositure (0-1m) for ",cur_mon_nam," relative to climate average of", cur_mon_only, "1981 - 2010.")

# Extract the desired path from plot_paths_df
prcp_rh_sm_ano_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_prcp_rh_sm_anomalies")) %>%
  pull(path)

knitr::include_graphics(prcp_rh_sm_ano_path)
```

### Last 12 months anomaly: `r prv_mon_nam` to `r cur_mon_nam`

```{r fig_prcp_rh_sm_ano_path12}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-prcp_rh_sm_ano12
#| fig-cap: !expr paste("Anomalies in total precipitation, relative humidity and volumetric soil moisture (0-1m) for ",prv_mon_nam, "to", cur_mon_nam," relative to climate average of 1981 - 2010.")

prcp_rh_sm_ano_path12 <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_prcp_rh_sm_last12months_anomalies")) %>%
  pull(path)

knitr::include_graphics(prcp_rh_sm_ano_path12)
```

### Long term trends

#### Spatial trends: `r format(as.Date(curr_mon_yr), "%B")` 1950 - `r update_year`

```{r fig_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of precipitation, relative humidity, and soil moisture anomalies for", cur_mon_nam ,":1950 - ",cur_yr_nam, ".The black dots indicate grid cells with statistically signficnat trends. Anomalies are calcuated relative to 1981-2010 climatology")

prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_prcp_rh_sm_longterm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(prcp_rh_sm_sptrn_path)
```

#### Time series trends: `r format(as.Date(curr_mon_yr), "%B")` 1950 - `r update_year`

```{r fig_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of precipitation, relative humidity and soil moisture for", cur_mon_nam ,":1950 - ",cur_yr_nam, ". Anomalies are calcuated relative to 1981-2010 climatology")

prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0(update_month, '_', update_year,"_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(prcp_rh_sm_tstrn_path)
```

## BC seasonal and annual climate trends

Below you find a summary table and the spatial and long term trend plots of air temperature, vapor pressure deficit (VPD), total monthly precipitation, relative humidity (RH), and volumetric soil moisture (0 - 1m depth) for each season and annual data.

```{r mon sea ann summary table }
#| include: false
#| cache: false

sea_summary_tbl <- result_fls_pth %>%
  filter(str_detect(result_pth , paste0('sea_ann_anomalies_trend_summaries_all_par_',update_year,'\\.csv$'))) 
sea_summary_tbl

sea_summary_f  <- read_csv(sea_summary_tbl$result_pth)
sea_summary_f
```

### Winter

```{r  sea win sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_win_sum_tab_f <- sea_summary_f%>%
  dplyr::filter(seaa == 'winter')

sea_yr <- unique(clm_win_sum_tab_f$yr)

clm_win_sum_tab_f%<>%
  dplyr::select(-c(yr,seaa))%<>%
  mutate(ano_rnk_pos = as.integer(ano_rnk_pos))
clm_win_sum_tab_f

clm_win_sum_tab_f%<>%
      dplyr::select(Parameter = par,
                    'Spatial average anomaly' = mean_ano,
                    'Spatial minimum anomaly' = min_ano,
                    'Spatial maximum anomaly' = max_ano,
                    'Average anomaly ranking' = ano_rnk_pos,
                    'Spatial average trend' = mean_trn,
                    'Spatial minimum trend' = min_trn,
                    'Spatial maximum trend' = min_trn,
                    'Linear trend' = lin_trn,
                    'Linear trend p-val'= lin_trn_pval)

clm_win_sum_tab_f%>%
  pivot_longer(cols = c(-Parameter), names_to = "nam", values_to = 'val')%>%
  pivot_wider(names_from = "Parameter", values_from = 'val')%>%
  dplyr::select('Measures' = nam,'Mean Temperature'=tmean, 'Precipitation'= prcp,
                'Vapour pressure deficiet (VPD)'=vpd,
                'Relative Humidity' = rh, 'Soil moisture'= soil_moisture) -> clm_win_sum_tab_ff

```

```{r  sea win sumamry table }
#| include: true
#| output: true
#| cache: false
#| label: tbl-bc_sea_win_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of winter ", sea_yr, 
#|                       ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", sea_yr, ".")

kbl(clm_win_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

#### Mean temperature and VPD

##### Spatial trends

```{r fig_win_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-win_tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of  mean temperature and VPD for winter:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
win_tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("winter_tmean_vpd_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(win_tmean_vpd_sptrn_path)
```

##### Time-series trends

```{r fig_win_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-win_tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for winter:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
win_tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("winter_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(win_tmean_vpd_tstrn_path)
```


#### Precipitation, relative humidity and soil moisture

##### Spatial trends

```{r fig_win_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-win_prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of precipitation, relative humidity, and soil mositure for winter:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
win_prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("winter_prcp_rh_sm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(win_prcp_rh_sm_sptrn_path)
```

##### Time-series trends

```{r fig_win_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-win_prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  precipitation, relative humidity and soil mositure for winter:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
win_prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("winter_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(win_prcp_rh_sm_tstrn_path)
```


### Spring

```{r  sea spr sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_spr_sum_tab_f <- sea_summary_f%>%
  filter(seaa == 'spring')
sea_yr <- unique(clm_spr_sum_tab_f$yr)

clm_spr_sum_tab_f%<>%
  dplyr::select(-c(yr,seaa))%<>%
  mutate(ano_rnk_pos = as.integer(ano_rnk_pos))
clm_spr_sum_tab_f

clm_spr_sum_tab_f%<>%
      dplyr::select(Parameter = par,
                    'Spatial average anomaly' = mean_ano,
                    'Spatial minimum anomaly' = min_ano,
                    'Spatial maximum anomaly' = max_ano,
                    'Average anomaly ranking' = ano_rnk_pos,
                    'Spatial average trend' = mean_trn,
                    'Spatial minimum trend' = min_trn,
                    'Spatial maximum trend' = min_trn,
                    'Linear trend' = lin_trn,
                    'Linear trend p-val'= lin_trn_pval)

clm_spr_sum_tab_f%>%
  pivot_longer(cols = c(-Parameter), names_to = "nam", values_to = 'val')%>%
  pivot_wider(names_from = "Parameter", values_from = 'val')%>%
  dplyr::select('Measures' = nam,'Mean Temperature'=tmean, 'Precipitation'= prcp,
                'Vapour pressure deficiet (VPD)'=vpd,
                'Relative Humidity' = rh, 'Soil moisture'= soil_moisture) -> clm_spr_sum_tab_ff

```

```{r  sea spr sumamry table }
#| include: true
#| output: true
#| cache: false
#| label: tbl-bc_sea_spr_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of spring ", sea_yr, 
#|                       ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", sea_yr, ".")

kbl(clm_spr_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

#### Mean temperature and VPD

##### Spatial trends

```{r fig_spr_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-spr_tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of  mean temperature and VPD for spring:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
spr_tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("spring_tmean_vpd_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(spr_tmean_vpd_sptrn_path)
```

##### Time-series trends

```{r fig_spr_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-spr_tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for spring:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
spr_tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("spring_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(spr_tmean_vpd_tstrn_path)
```


#### Precipitation, relative humidity and soil moisture

##### Spatial trends

```{r fig_spr_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-spr_prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of precipitation, relative humidity, and soil mositure for spring:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
spr_prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("spring_prcp_rh_sm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(spr_prcp_rh_sm_sptrn_path)
```

##### Time-series trends

```{r fig_spr_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-spr_prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  precipitation, relative humidity and soil mositure for spring:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
spr_prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("spring_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(spr_prcp_rh_sm_tstrn_path)
```


### Summer

```{r  sea sum sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_sum_sum_tab_f <- sea_summary_f%>%
  filter(seaa == 'summer')
sea_yr <- unique(clm_sum_sum_tab_f$yr)

clm_sum_sum_tab_f%<>%
  dplyr::select(-c(yr,seaa))%<>%
  mutate(ano_rnk_pos = as.integer(ano_rnk_pos))
clm_sum_sum_tab_f

clm_sum_sum_tab_f%<>%
      dplyr::select(Parameter = par,
                    'Spatial average anomaly' = mean_ano,
                    'Spatial minimum anomaly' = min_ano,
                    'Spatial maximum anomaly' = max_ano,
                    'Average anomaly ranking' = ano_rnk_pos,
                    'Spatial average trend' = mean_trn,
                    'Spatial minimum trend' = min_trn,
                    'Spatial maximum trend' = min_trn,
                    'Linear trend' = lin_trn,
                    'Linear trend p-val'= lin_trn_pval)

clm_sum_sum_tab_f%>%
  pivot_longer(cols = c(-Parameter), names_to = "nam", values_to = 'val')%>%
  pivot_wider(names_from = "Parameter", values_from = 'val')%>%
  dplyr::select('Measures' = nam,'Mean Temperature'=tmean, 'Precipitation'= prcp,
                'Vapour pressure deficiet (VPD)'=vpd,
                'Relative Humidity' = rh, 'Soil moisture'= soil_moisture) -> clm_sum_sum_tab_ff

```

```{r  sea sum sumamry table }
#| include: true
#| output: true
#| cache: false
#| label: tbl-bc_sea_sum_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of summer ", sea_yr, 
#|                       ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", sea_yr, ".")

kbl(clm_sum_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

#### Mean temperature and VPD

##### Spatial trends

```{r fig_sum_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-sum_tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of  mean temperature and VPD for summer:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
sum_tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("summer_tmean_vpd_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(sum_tmean_vpd_sptrn_path)
```

##### Time-series trends

```{r fig_sum_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-sum_tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for summer:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
sum_tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("summer_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(sum_tmean_vpd_tstrn_path)
```


#### Precipitation, relative humidity and soil moisture

##### Spatial trends

```{r fig_sum_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-sum_prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of precipitation, relative humidity, and soil mositure for summer:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
sum_prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("summer_prcp_rh_sm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(sum_prcp_rh_sm_sptrn_path)
```

##### Time-series trends

```{r fig_sum_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-sum_prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  precipitation, relative humidity and soil mositure for summer:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
sum_prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("summer_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(sum_prcp_rh_sm_tstrn_path)
```




### Fall

```{r  sea fal sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_fal_sum_tab_f <- sea_summary_f%>%
  filter(seaa == 'fall')
sea_yr <- unique(clm_fal_sum_tab_f$yr)

clm_fal_sum_tab_f%<>%
  dplyr::select(-c(yr,seaa))%<>%
  mutate(ano_rnk_pos = as.integer(ano_rnk_pos))
clm_fal_sum_tab_f

clm_fal_sum_tab_f%<>%
      dplyr::select(Parameter = par,
                    'Spatial average anomaly' = mean_ano,
                    'Spatial minimum anomaly' = min_ano,
                    'Spatial maximum anomaly' = max_ano,
                    'Average anomaly ranking' = ano_rnk_pos,
                    'Spatial average trend' = mean_trn,
                    'Spatial minimum trend' = min_trn,
                    'Spatial maximum trend' = min_trn,
                    'Linear trend' = lin_trn,
                    'Linear trend p-val'= lin_trn_pval)

clm_fal_sum_tab_f%>%
  pivot_longer(cols = c(-Parameter), names_to = "nam", values_to = 'val')%>%
  pivot_wider(names_from = "Parameter", values_from = 'val')%>%
  dplyr::select('Measures' = nam,'Mean Temperature'=tmean, 'Precipitation'= prcp,
                'Vapour pressure deficiet (VPD)'=vpd,
                'Relative Humidity' = rh, 'Soil moisture'= soil_moisture) -> clm_fal_sum_tab_ff

```

```{r  sea fal sumamry table }
#| include: true
#| output: true
#| cache: false
#| label: tbl-bc_sea_fal_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of fall ", sea_yr, 
#|                       ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", sea_yr, ".")

kbl(clm_fal_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

#### Mean temperature and VPD

##### Spatial trends

```{r fig_fal_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-fal_tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of  mean temperature and VPD for fall:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
fal_tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("fall_tmean_vpd_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(fal_tmean_vpd_sptrn_path)
```

##### Time-series trends

```{r fig_fal_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-fal_tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for fall:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
fal_tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("fall_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(fal_tmean_vpd_tstrn_path)
```


#### Precipitation, relative humidity and soil moisture

##### Spatial trends

```{r fig_fal_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-fal_prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of precipitation, relative humidity, and soil mositure for fall:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
fal_prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("fall_prcp_rh_sm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(fal_prcp_rh_sm_sptrn_path)
```

##### Time-series trends

```{r fig_fal_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-fal_prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  precipitation, relative humidity and soil mositure for fall:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
fal_prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("fall_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(fal_prcp_rh_sm_tstrn_path)
```


### Annual

```{r  sea ann sumamry table process}
#| include: false
#| output: true
#| cache: false

clm_ann_sum_tab_f <- sea_summary_f%>%
  filter(seaa == 'annual')
sea_yr <- unique(clm_ann_sum_tab_f$yr)

clm_ann_sum_tab_f%<>%
  dplyr::select(-c(yr,seaa))%<>%
  mutate(ano_rnk_pos = as.integer(ano_rnk_pos))
clm_ann_sum_tab_f

clm_ann_sum_tab_f%<>%
      dplyr::select(Parameter = par,
                    'Spatial average anomaly' = mean_ano,
                    'Spatial minimum anomaly' = min_ano,
                    'Spatial maximum anomaly' = max_ano,
                    'Average anomaly ranking' = ano_rnk_pos,
                    'Spatial average trend' = mean_trn,
                    'Spatial minimum trend' = min_trn,
                    'Spatial maximum trend' = min_trn,
                    'Linear trend' = lin_trn,
                    'Linear trend p-val'= lin_trn_pval)

clm_ann_sum_tab_f%>%
  pivot_longer(cols = c(-Parameter), names_to = "nam", values_to = 'val')%>%
  pivot_wider(names_from = "Parameter", values_from = 'val')%>%
  dplyr::select('Measures' = nam,'Mean Temperature'=tmean, 'Precipitation'= prcp,
                'Vapour pressure deficiet (VPD)'=vpd,
                'Relative Humidity' = rh, 'Soil moisture'= soil_moisture) -> clm_ann_sum_tab_ff

```

```{r  sea ann sumamry table }
#| include: true
#| output: true
#| cache: false
#| label: tbl-bc_sea_ann_clm_summary
#| tbl-cap: !expr paste0("BC climate summary of annual ", sea_yr, 
#|                       ". The average anomaly ranking (highest positive anomaly being 1) and trends are for 1950 - ", sea_yr, ".")

kbl(clm_ann_sum_tab_ff, font_size = 25) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    font_size = 20,
    fixed_thead = TRUE
  ) %>%
  column_spec(1, bold = TRUE, border_right = TRUE)

```

#### Mean temperature and VPD

##### Spatial trends

```{r fig_ann_tmean_vpd_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-ann_tmean_vpd_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of  mean temperature and VPD for annual:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
ann_tmean_vpd_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("annual_tmean_vpd_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(ann_tmean_vpd_sptrn_path)
```

##### Time-series trends

```{r fig_ann_tmean_vpd_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-ann_tmean_vpd_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  mean temperature and VPD for annual:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
ann_tmean_vpd_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("annual_tmean_vpd_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(ann_tmean_vpd_tstrn_path)
```


#### Precipitation, relative humidity and soil moisture

##### Spatial trends

```{r fig_ann_prcp_rh_sm_sptrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-ann_prcp_rh_sm_sptrn
#| fig-cap: !expr paste("Spatial trends of the anomalies of precipitation, relative humidity, and soil mositure for annual:1950 - ",sea_yr, ".The black dots indicate grids with significant trends. Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
ann_prcp_rh_sm_sptrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("annual_prcp_rh_sm_spatial_trend")) %>%
  pull(path)

knitr::include_graphics(ann_prcp_rh_sm_sptrn_path)
```

##### Time-series trends

```{r fig_ann_prcp_rh_sm_tstrn_path}
#| include: true
#| output: true
#| cache: true
#| fig-align: center
#| label: fig-ann_prcp_rh_sm_tstrn
#| fig-cap: !expr paste("Trend in spatially averaged anomalies of  precipitation, relative humidity and soil mositure for annual:1950 - ",sea_yr, ". Anomalies are calcuated relative to 1981-2010 climatology.")

# Extract the desired path from plot_paths_df
ann_prcp_rh_sm_tstrn_path <- plot_paths_df %>%
  filter(plot_type == paste0("annual_prcp_rh_sm_bc_timeseries_trend")) %>%
  pull(path)

knitr::include_graphics(ann_prcp_rh_sm_tstrn_path)
```


This report compliment the <a href='https://bcgov-env.shinyapps.io/bc_climate_anomaly/'> BC climate anomaly app </a>. Should you have any questions, please contact <a href= 'mailto: Aseem.Sharma@gov.bc.ca'>Aseem Sharma </a>.

::: {style="font-size: 60%;"}
**Disclaimer:** This report has been prepared using <a href='https://www.ecmwf.int/en/era5-land'>ERA5-Land</a> data from the European Centre for Medium-Range Weather Forecasts (ECMWF), as available at the time of preparation. Please note that the original data may be subject to updates or revisions. Any modifications to the original data may result in adjustments to the findings presented in this report.
:::
