---
title: "BC annual climate report for 2025"
author:
 name: "Aseem Sharma e-mail: aseem.sharma@gov.bc.ca"
 corresponding: true
 email: Aseem.Sharma@gov.bc.ca
 affiliations:
    id: "FFEC"
    name: "Future Forest Ecosystems Centre (FFEC), Forest Ecosystems and Analytics (FEA), BC Ministry of Forests" 
date: "`r paste('Date:', format(Sys.time(), '%d %B, %Y'))`"
code-annotations: false
execute:
  echo: false
  warning: false
  output: false
cap-location: bottom
editor: visual
wrap: auto
format: 
 html:
  fig-format: png
  toc_float: true
  toc-location: left
  toc: true
  toc-depth: 6
  toc-title: "Contents"
  number-sections: true
  number-depth: 0
  table-cap-location: top
  embed-resources: true
  self-contained: true
  theme: united 
  css: style.css
#  pdf:
#   lof: true
#   lot: false
#   number-sections: false
#   fig-pos: 'H'
#   fig-format: png
#   fig-dpi: 150
#   pdf-engine: latexmk
#   pdf-engine-opt: -xelatex
# editor_options:
#  chunk_output_type: console
editor_options: 
  chunk_output_type: console
---

```{=html}
<!-- 
below modfies the quarto to create print to pdf button and change HTML document to print friendly by changing the format.
-->
```

::: print-button-container
<button id="printButton" class="print-button">

Print to PDF

</button>
:::

```{=html}
<style>
/* General styles for the browser view (from Quarto theme) are untouched */

.print-button-container {
  margin-top: 20px;
  text-align: right;
}

.print-button {
  background-color: #007bff;
  color: white;
  border: none;
  padding: 10px 15px;
  font-size: 14px;
  border-radius: 5px;
  cursor: pointer;
}

.print-button:hover {
  background-color: #0056b3;
}

/* Print-specific styles (only active when .print-mode is applied) */
.print-mode body {
  background-color: white;
  color: black;
  font-size: 12pt;
}

.print-mode .print-button-container {
  display: none; /* Hide the print button during printing */
}

.print-mode h1, .print-mode h2, .print-mode h3 {
  page-break-after: avoid;
}

.print-mode p {
  margin: 1em 0;
}

.print-mode table {
  width: 100%;
  border-collapse: collapse;
}

.print-mode th, .print-mode td {
  border: 1px solid #000;
  padding: 5px;
}
</style>
```

```{=html}
<script>
document.getElementById("printButton").addEventListener("click", function () {
  // Add the print-specific class to the <html> element
  document.documentElement.classList.add("print-mode");

  // Trigger the print dialog
  window.print();

  // Remove the print-specific class after a brief delay
  setTimeout(function () {
    document.documentElement.classList.remove("print-mode");
  }, 1000);
});
</script>
```

```{r}
#| label: setup
#| include: false
knitr::opts_chunk$set(echo = FALSE, dpi = 400)
```

```{r required}
#| include: false
#| results: hold
#| cache: false

# Required -------------------------------
rqr_pkgs <-
  c(
    'terra',
    'sf',
    'bcmaps',
    "tidyverse",
    'lubridate',
    'gt',
    'zoo',
    'magrittr',
    "Kendall",
    "zyp",
    "tidyterra",
    "colorspace",
    "cptcity",
    "quarto",
    'patchwork',
    'kableExtra',
    'purrr',
    'furrr'
      )
# Install packages if not
installed_rqr_pkgs <- rqr_pkgs %in% rownames(installed.packages())
if (any(installed_rqr_pkgs == FALSE)) {
  install.packages(rqr_pkgs[!installed_rqr_pkgs])
}
# Load:
lapply(rqr_pkgs , require, character.only = TRUE)

# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
```

```{r paths}
#| include: false
#| results: 'hold'
#| cache: false
# Paths ------------------------
# setwd(getwd())
shp_fls_pth <- '../../data_database/data_shapefiles/'
ano_dt_pth <-  '../ano_clm_trn_data/'
ann_summ_rslts_pth <- './annual_summary_results/'

```

```{r datafiles requirements }
#| include: false
#| cache: false

# Data files ------------------
# Shape files --------------------------------
# Domain Shape files
xmi = -140
xmx = -108
ymi = 39
ymx = 60

# BC plot limit
xlim <- c(-140, -113)
ylim <- c(47.5, 60)

# Update year
cur_yr <- as.character(as.integer(format(Sys.Date(), "%Y")) - 1)

# List of shape files
list.files(path = shp_fls_pth,
           pattern = ".gpkg",
           full.names = T) -> shp_fls_lst
shp_fls_lst

# BC
bc_shp <- vect(shp_fls_lst[str_detect(shp_fls_lst,"bc_shapefile")== T])
plot(bc_shp)
bc_shp_prj <- project(bc_shp, "+proj=aea +lat_0=45 +lon_0=-126 +lat_1=50 +lat_2=58.5 +x_0=1000000 +y_0=0 +datum=NAD83 +units=m +no_defs")
plot(bc_shp_prj)

## Months, parameters ----
months_nam <-
  c(
    "annual",
    "winter",
    "spring",
    "summer",
    "fall",
    "Jan",
    "Feb",
    "Mar",
    "Apr",
    "May",
    "Jun",
    "Jul",
    "Aug",
    "Sep",
    "Oct",
    "Nov",
    "Dec"
  )
months_nam

parameters <- c("tmean",  "prcp","soil_moisture")
parameters


## Anomalies Data files -----
ano_dt_fls <- list.files(
  path = ano_dt_pth,
  pattern = ".*_ano_.*\\.nc",
  full.names = TRUE
) %>%
  tibble(dt_pth = .) %>%
  mutate(
    mon = str_extract(dt_pth, paste(months_nam, collapse = "|")),
    par = str_extract(dt_pth, paste(parameters, collapse = "|"))
  ) %>%
  drop_na()
ano_dt_fls


## Climatology Data files -----
clm_dt_fls <- list.files(
  path = ano_dt_pth,
  pattern = ".*_clm_.*\\.nc",
  full.names = TRUE
) %>%
  tibble(dt_pth = .) %>%
  mutate(
     mon = str_extract(dt_pth, paste(months_nam, collapse = "|")),
    par = str_extract(dt_pth, paste(parameters, collapse = "|"))
  ) %>%
  drop_na() 
clm_dt_fls

```

```{r analysis summary plot funtions}
#| include: false
#| cache: false

# Anomalies analysis and plots --------------
months_nam
# Annual and monthly climate summary calculations and plot function ------
ann_clm_summ_cal_plt_fun <- function(
    ano_dt_fls,
    clm_dt_fls,
    bc_shp,
    parr,
    cur_yr, region
) {


  # parr <- 'tmean'

  ### metadata -----------------------------------------------------------
  par_meta <- tibble::tribble(
    ~par,            ~par_full,                          ~unit,
    "tmin",          "Minimum temperature",              "°C",
    "tmax",          "Maximum temperature",              "°C",
    "tmean",         "Average temperature",              "°C",
    "prcp",          "Precipitation",                    "%",
    "rh",            "Relative Humidity (RH)",           "%",
    "vpd",           "Vapor Pressure Deficit (VPD)",     "kPa",
    "soil_moisture", "Volumetric soil moisture (0–1 m)", "%"
  )

  meta <- par_meta |> filter(par == parr)
  parr_full <- meta$par_full
  unt <- meta$unit

  ## helper functions ---------------------------------------------------------

  ### Calculation helper functions --------------
  # Percentage of anomaly

  calc_percent_anomaly <- function(ano, clm) {
  ano_r_per <- (ano / clm) * 100
  # ano_r_per <- clamp(ano_r_per, -101,101,values =T)
  return(ano_r_per)
  }

  # Function to calculate summaries
  spatial_summ_fun <- function(
    rast_dt
  ) {

    # rast_dt <- mon_cur_yr_dt
    ## spatial summaries (mean / min / max)
    sp_mean <- global(rast_dt, "mean", na.rm = TRUE)
    sp_min  <- global(rast_dt, "min",  na.rm = TRUE)
    sp_max  <- global(rast_dt, "max",  na.rm = TRUE)

    summ_tbl <- tibble(
      rst_fl  = rownames(sp_mean),
      mean = round(sp_mean[, 1], 2),
      min  = round(sp_min[, 1],  2),
      max  = round(sp_max[, 1],  2)
    ) %>%
      mutate(
        yr = cur_yr
      )

    summ_tbl
  }


  # Spatial Mann-kendall trends
  # Calculate MK trend
  mk_pval_fun <- function(x) {
    if (all(is.na(x))) return(NA_real_)
    MannKendall(x)[[2]]
  }
  sen_slope_fun <- function(x) {
    if (all(is.na(x))) return(NA_real_)
    zyp.trend.vector(x, conf.intervals = FALSE)[[2]]
  }


  ### Plotting helper functions -------------

  calc_sym_breaks <- function(minval, maxval) {
    # Find the largest absolute value
    rng <- max(abs(minval), abs(maxval))

    # Determine step size based on range
    step <- dplyr::case_when(
      rng < 5   ~ 0.5,
      rng < 11  ~ 1,
      rng < 21  ~ 2,
      rng < 41  ~ 5,
      rng < 101 ~ 10,
      TRUE      ~ 20
    )

    # Compute symmetric breaks
    lower <- -ceiling(rng / step) * step
    upper <-  ceiling(rng / step) * step

    seq(lower, upper, by = step)
  }

  ###  Raster Map plot theme  and guide

  theme_bc_map <- function(nlyr = 1) {
    theme(
      # Panel
      panel.spacing = unit(0.1, "lines"),
      panel.grid.minor = element_blank(),
      panel.grid.major = element_line(
        color = "gray60",
        linewidth = 0.02,
        linetype = "dashed"
      ),
      axis.line = element_line(colour = "gray70", linewidth = 0.08),

      # Axis ticks
      axis.ticks.length = unit(-0.20, "cm"),
      axis.ticks = element_line(colour = "black", linewidth = 1),

      # # Axis titles
      # axis.title.x = element_text(
      #   angle = 0, face = "plain", size = 15,
      #   colour = "black",
      #   margin = margin(t = 0, r = 0, b = 0, l = 0)
      # ),
      # axis.title.y = element_text(
      #   angle = 90, face = "plain", size = 15,
      #   colour = "black",
      #   margin = margin(t = 0, r = 0, b = 0, l = 0)
      # ),
      #
      # # Axis text
      # axis.text.x = element_text(
      #   angle = 0, hjust = 0.5, vjust = 0.5,
      #   colour = "black", size = 14,
      #   margin = margin(t = 2, r = 2, b = 2, l = 2)
      # ),
      # axis.text.y = element_text(
      #   angle = 90, hjust = 0.5, vjust = 0.5,
      #   colour = "black", size = 14,
      #   margin = margin(t = 2, r = 2, b = 2, l = 2)
      # ),

      # Plot title
      plot.title = element_text(angle = 0, face = "bold", size = 13, colour = "black"),

      # Facet strips
      strip.background = element_rect(color = "black", fill = "white"),
      strip.text.x = element_text(size = 12, angle = 0, face = "bold"),
      strip.text.y = element_text(size = 12, face = "bold"),

      # Legend
      legend.position = if(nlyr == 1) c(0.2, 0.4) else "right",
      legend.direction = "vertical",
      legend.margin = margin(t = 0, r = 0, b = 0, l = 0),
      legend.box.margin = margin(t = -5, r = -5, b = -5, l = -5),
      legend.title = element_text(size = 15),
      legend.text = element_text(size = 16, margin = margin(t = 0, r = 0, b = 0, l = 0)),

      # General axis.text margin (removed negative to avoid warnings)
      axis.text = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0)),
      panel.background = element_rect(fill = "white"),
      plot.background  = element_rect(fill = "white"),

      # Remove axis text
      axis.title.x = element_blank(),
      axis.text.x = element_blank(),
      axis.ticks.x = element_blank(),
      axis.title.y = element_blank(),
      axis.text.y = element_blank(),
      axis.ticks.y = element_blank()
    )
  }

  # Guide bar

  fill_guide <- guide_colorbar(
    barwidth = 1.5,
    barheight = 22,
    label.vjust = 0.5,
    label.hjust = 0.0,
    title.vjust = 0.5,
    title.hjust = 0.5,
    title = NULL,
    ticks.colour = 'black',
    frame.colour = 'black',
    draw.ulim = TRUE,
    draw.llim = TRUE,
  )

  ### Linear time series plot theme
  theme_ts_linear <- function(
    legend_pos = c(0.5, 0.08),
    legend_dir = "horizontal"
  ) {
    theme_bw() +
      theme(
        # Grid
        panel.grid.minor = element_blank(),
        panel.grid.major = element_line(
          color = "gray75",
          linewidth = 0.03,
          linetype = "dashed"
        ),

        # Axes
        axis.line = element_line(colour = "black", linewidth = 1),
        axis.ticks = element_line(colour = "black", linewidth = 1),
        axis.ticks.length = unit(-0.20, "cm"),

        axis.title.x = element_text(
          size = 13, colour = "black",
          margin = margin(t = 3)
        ),
        axis.title.y = element_text(
          size = 13, colour = "black",
          margin = margin(r = 3)
        ),

        axis.text.x = element_text(
          angle = 90, size = 12, colour = "black",
          hjust = 0.5, vjust = 0.5,
          margin = margin(t = 2)
        ),
        axis.text.y = element_text(
          angle = 0, size = 12, colour = "black",
          hjust = 0.5, vjust = 0.5,
          margin = margin(r = 2)
        ),

        # Title
        plot.title = element_text(
          face = "bold", size = 13, colour = "black"
        ),
        plot.subtitle = element_text(size = 11),

        # Legend
        legend.position = legend_pos,
        legend.direction = legend_dir,
        legend.background = element_rect(fill = NA, color = "black"),
        legend.margin = margin(0, 0, 0, 0),
        legend.box.margin = margin(0, 0, 0, 0),
        legend.title = element_text(size = 13),
        legend.text = element_text(size = 13),

        # Facets (if used)
        strip.background = element_rect(fill = "black"),
        strip.text = element_text(size = 12, face = "bold", colour = "black"),

        # Tag / watermark
        plot.tag.position = "bottom",
        plot.tag = element_text(
          color = "gray50",
          size = 8,
          hjust = 1
        )
      )
  }

  ## Load raster data for quick calculations  ---------

 ano_dt_paths <- ano_dt_fls |>
    distinct(dt_pth) |>
    pull(dt_pth)
  ano_dt_paths

   # Add all rasters for quick calculations
  rast_ano_cache <- purrr::map(
    setNames(ano_dt_paths, ano_dt_paths),
    terra::rast
  )

  ## monthly spatial anomalies and summary --------------------------------------------------
  months <- c("Jan" ,"Feb", "Mar","Apr","May","Jun","Jul",
                        "Aug","Sep","Oct","Nov","Dec")

  ### Monthly anomaly & plots -----------------------

  mon_rasts <- map(months, function(mon_i) {

    ano_fl <- ano_dt_fls |> filter(mon == mon_i & par == parr)

    ano_r <- rast_ano_cache[[ano_fl$dt_pth]]


    clm_fl <- clm_dt_fls |> filter(mon == mon_i & par == parr)

    clm_r <- rast(clm_fl$dt_pth)

    if (parr %in% c("prcp", "soil_moisture")) {
      ano_r <- calc_percent_anomaly(ano_r, clm_r)
    }

    ano_r <- crop(ano_r, bc_shp, mask = TRUE)
  })

  mon_ano_dt_stk <- rast(mon_rasts)
  names(mon_ano_dt_stk)

  terra::time(mon_ano_dt_stk) <- as.Date(names(mon_ano_dt_stk), format= '%Y-%m-%d')
  mon_ano_dt_stk

  # Filter for current year
  mon_cur_yr_dt <- subset(
    mon_ano_dt_stk,
    format(as.Date(names(mon_ano_dt_stk)), "%Y") == cur_yr
  )
  names(mon_cur_yr_dt)
  mon_cur_yr_dt
 # plot(mon_cur_yr_dt)

 # Clamp anomaly percentage for above 100
 mon_cur_yr_dt <-  clamp( mon_cur_yr_dt, -101,101,values =T)

 # Monthly ano spatial plotting
 mon_cur_yr_dt <- project(mon_cur_yr_dt, crs(bc_shp_prj))
 mon_cur_yr_dt <- mask(mon_cur_yr_dt, bc_shp_prj)

 # Monthly  breaks
 mon_minval <- min(values(mon_cur_yr_dt), na.rm = TRUE)
 mon_maxval <- max(values(mon_cur_yr_dt), na.rm = TRUE)
 mon_brks   <- calc_sym_breaks(mon_minval, mon_maxval)

 mon_ano_plt <-  ggplot()+
 geom_spatraster(data = mon_cur_yr_dt)+
   scale_fill_gradientn(
     colours = cpt("ncl_BlWhRe", 100),
     limits = c((-1* max(abs(c(mon_minval, mon_maxval)))),
                (1* max(abs(c(mon_minval, mon_maxval))))),
     breaks = mon_brks,
     guide = fill_guide,
     na.value = "transparent"
   ) +
   facet_wrap(
     ~ factor(format(as.Date(lyr), "%b"), levels = month.abb),
     ncol = 4
   ) +
   geom_spatvector(data = bc_shp_prj, fill = NA, color = 'black', linewidth = 0.3)
 mon_ano_plt

 if (parr == "prcp" | parr == "soil_moisture"){
   mon_ano_plt <- mon_ano_plt  +
     scale_fill_gradientn(

       colours = cpt(pal = "cmocean_curl", n = 100, rev = T),
       limits = c((-1* abs(max(c(mon_minval, mon_maxval)))),
                  (1* abs(max(c(mon_minval, mon_maxval))))),
       breaks = mon_brks,
       guide = fill_guide,
       na.value = "transparent"
     )+
     theme_bc_map(nlyr = nlyr(mon_cur_yr_dt)) +
     labs(
       title = paste0(cur_yr, " Monthly Anomalies: ", parr_full ),
       subtitle = paste0(parr_full,' (', unt,' )', ' relative to 1981-2010 climatology')
     )
 } else {
   mon_ano_plt <- mon_ano_plt+
     theme_bc_map(nlyr = nlyr(mon_cur_yr_dt)) +
     labs(
       title = paste0(cur_yr, " Monthly Anomalies: ", parr_full ),
       subtitle = paste0(parr_full,' (', unt,' )', ' relative to 1981-2010 climatology')
     )
 }
 mon_ano_plt

 ggsave(
   paste0(
     ann_summ_rslts_pth, parr,
     '_monthly_spatial_anomaly_maps_plt_',
     cur_yr,'.png'
   ),
   plot = mon_ano_plt,
   width = 13,
   height = 9.5,
   units = "in",
   dpi = 350,
   scale = 0.9,
   limitsize = F
 )

 ### Monthly spatial anomaly summary ---------------------
 mon_summ_tbl <- spatial_summ_fun(
   rast_dt = mon_cur_yr_dt
 )
 mon_summ_tbl %>%
   mutate(parr = parr) %>%
   mutate(
     rst_fl = as.Date(rst_fl),
     mon = factor(month(rst_fl, label = TRUE, abbr = TRUE),
                  levels = month.abb)
   ) %>%
   rename(type_prd = rst_fl) -> mon_summ_tbl
 mon_summ_tbl


 ## Annual spatial and time series anomaly -----------------------------------------------------
 # annual raster data
 ann_ano_fl <- ano_dt_fls |> filter(mon == 'annual' & par == parr)

 ann_ano_r <- rast_ano_cache[[ann_ano_fl$dt_pth]]

 ann_clm_fl <- clm_dt_fls |> filter(mon == 'annual' & par == parr)
 ann_clm_r <- rast(ann_clm_fl$dt_pth)

 if (parr %in% c("prcp", "soil_moisture")) {
   ann_ano_r <- calc_percent_anomaly(ann_ano_r, ann_clm_r)
 } else {
   ann_ano_r <- ann_ano_r
 }

 ann_ano_r <- crop(ann_ano_r, bc_shp, mask = TRUE)
 names(ann_ano_r)

 yrs <- str_remove(names(ann_ano_r), "^ann_") |> as.integer()
 names(ann_ano_r) <- yrs

 ### Annual spatial anomaly plot and summary -------------------
 ann_ano_r_cur_yr <- subset(ann_ano_r, which(names(ann_ano_r) %in% cur_yr))
 ann_ano_r_cur_yr
# pann_ano_r_cur_yrlot(ann_ano_r_cur_yr)
 # Spatial Plot
 # Clamp anomaly percentage for above 100
 ann_ano_r_cur_yr <-  clamp(ann_ano_r_cur_yr, -101,101,values =T)

  # breaks
 ann_minval <- min(values(ann_ano_r_cur_yr), na.rm = TRUE)
 ann_maxval <- max(values(ann_ano_r_cur_yr), na.rm = TRUE)
 ann_brks   <- calc_sym_breaks(ann_minval, ann_maxval)

 ann_ano_r_cur_yr <- project(ann_ano_r_cur_yr, crs(bc_shp_prj))
 ann_ano_r_cur_yr <- mask(ann_ano_r_cur_yr, bc_shp_prj)

 yr_ann_sp_ano_plt <-  ggplot()+
   geom_spatraster(data = ann_ano_r_cur_yr)+
   scale_fill_gradientn(
     colours = cpt("ncl_BlWhRe", 100),
     limits = c((-1* max(abs(c(ann_minval, ann_maxval)))),
                (1* max(abs(c(ann_minval, ann_maxval))))),
     breaks = ann_brks,
     guide = fill_guide,
     na.value = "transparent"
   ) +
   # facet_wrap(
   #   ~ factor(format(as.Date(lyr), "%b"), levels = month.abb),
   #   ncol = 4
   # ) +
   geom_spatvector(data = bc_shp_prj, fill = NA, color = 'black', linewidth = 0.3)
 yr_ann_sp_ano_plt

 if (parr == "prcp" | parr == "soil_moisture"){
   yr_ann_sp_ano_plt <- yr_ann_sp_ano_plt  +
     scale_fill_gradientn(

       colours = cpt(pal = "cmocean_curl", n = 100, rev = T),
       limits = c((-1* max(abs(c(ann_minval, ann_maxval)))),
                  (1* max(abs(c(ann_minval, ann_maxval))))),
       breaks = ann_brks,
       guide = fill_guide,
       na.value = "transparent"
     )+
     theme_bc_map(nlyr = nlyr(ann_ano_r_cur_yr)) +
     labs(
       title = paste0(cur_yr, " Annual Anomalies: ", parr_full ),
       subtitle = paste0(parr_full,' (', unt,' of normal)', ' relative to 1981-2010 climatology')
     )
 } else {
   yr_ann_sp_ano_plt  <-  yr_ann_sp_ano_plt +
     theme_bc_map(nlyr = nlyr(ann_ano_r_cur_yr)) +
     labs(
       title = paste0(cur_yr, " Annual Anomalies: ", parr_full ),
       subtitle = paste0(parr_full,' (', unt,' )', ' relative to 1981-2010 climatology')
     )
 }
 yr_ann_sp_ano_plt

 ggsave(
   paste0(
     ann_summ_rslts_pth, parr,
     '_annual_spatial_anomaly_maps_plt_',
     cur_yr,'.png'
   ),
   plot = yr_ann_sp_ano_plt,
   width = 11,
   height = 9.5,
   units = "in",
   dpi = 350,
   scale = 0.9,
   limitsize = F
 )

 ###  Annual anomaly spatial summary of current year --------------------------
 ann_ano_sp_summ_tbl <- spatial_summ_fun(
   rast_dt = ann_ano_r_cur_yr
 )
 ann_ano_sp_summ_tbl %>%
   mutate(parr = parr) %>%
   mutate(mon = 'ann') %>%
   mutate(type_prd = paste0(cur_yr,'_ann_ano_sp')) %>%
  dplyr::select(-rst_fl) -> ann_ano_sp_summ_tbl
 ann_ano_sp_summ_tbl

 ### Annual anomaly spatial trend summary ------------------------
 # Calculate spatial trend and rate of change summary
 # Spatial trend 1950 -now

 ann_ano_r_1950 <- ann_ano_r[[which(as.numeric(names(ann_ano_r)) >= 1950)]]

 sp_trn_mag_1950 <- app(ann_ano_r_1950, sen_slope_fun)
 sp_trn_sig_1950 <- app(ann_ano_r_1950, mk_pval_fun)

 sp_trn_1950 <- c(sp_trn_mag_1950, sp_trn_sig_1950)
 names(sp_trn_1950) <- c("ann_ano_sp_sen_slope_1950", "ann_ano_sp_mk_pval_1950")

 # Spatial trend  1980 -now
 ann_ano_r_1980 <- ann_ano_r[[which(as.numeric(names(ann_ano_r)) >= 1980)]]

 sp_trn_mag_1980 <- app(ann_ano_r_1980, sen_slope_fun)
 sp_trn_sig_1980 <- app(ann_ano_r_1980, mk_pval_fun)

 sp_trn_1980 <- c(sp_trn_mag_1980, sp_trn_sig_1980)
 names(sp_trn_1980) <- c("ann_ano_sp_sen_slope_1980", "ann_ano_sp_mk_pval_1980")
 # plot(sp_trn_1980)

 ann_sp_trns_dt <- c(sp_trn_1950, sp_trn_1980)

 # Spatial trend summary
 ann_sp_trn_summ_tbl <- spatial_summ_fun(
   rast_dt = ann_sp_trns_dt
 )
 ann_sp_trn_summ_tbl%>%
   mutate(parr = parr) %>%
   mutate(mon = 'ann'
   )%>%
   rename(type_prd = rst_fl) -> ann_sp_trn_summ_tbl
 ann_sp_trn_summ_tbl

 ### Spatial y averaged time series anomaly and trend plot ----------------------
 ano_ann_ts_dt <- tibble(
   yr  = as.numeric(names(ann_ano_r)),
   ano = global(ann_ano_r, "mean", na.rm = TRUE)[, 1]
 ) %>%
   drop_na() %>%
   mutate(par = parr)

# Time series trends
# Mean trend 1950s
 ann_ts_trn_1950 <- zyp.sen(ano ~ yr,  ano_ann_ts_dt  %>% filter(yr >= 1950))

 ann_ts_trn_1950_tbl <- tibble(
   type_prd = "1950-ts-summ-trn",
   slope  = ann_ts_trn_1950$coefficients[[2]],
   intercept = ann_ts_trn_1950$coefficients[[1]],
   mk_pval = MannKendall(
     ano_ann_ts_dt%>% filter(yr >= 1950) %>% pull(ano)
   )[[2]]
 ) %>%
   mutate(parr = parr, mon = 'ann')

 # Mean trend 1980s
 ann_ts_trn_1980 <- zyp.sen(ano ~ yr,  ano_ann_ts_dt  %>% filter(yr >= 1980))

 ann_ts_trn_1980_tbl <- tibble(
   type_prd = "1980-ts-summ-trn",
   slope  = ann_ts_trn_1980$coefficients[[2]],
   intercept = ann_ts_trn_1980$coefficients[[1]],
   mk_pval = MannKendall(
     ano_ann_ts_dt%>% filter(yr >= 1980) %>% pull(ano)
   )[[2]]
 ) %>%
   mutate(parr = parr,
          mon = 'ann')

 # Final annual summary table
 ann_trn_summ_tbl <- bind_rows(
   ann_ts_trn_1950_tbl,
   ann_ts_trn_1980_tbl
 )
 ann_trn_summ_tbl %>%
   mutate( min = min(ano_ann_ts_dt$ano,na.rm=T),
           max = max(ano_ann_ts_dt$ano,na.rm=T),
           mean = mean(ano_ann_ts_dt$ano,na.rm=T),
           yr = cur_yr ) ->  ann_trn_summ_tbl
 ann_trn_summ_tbl

 # Time series plot
 ano_ann_ts_dt

 ann_ts_minval <- -max(abs(ano_ann_ts_dt$ano))
 ann_ts_maxval <-  max(abs(ano_ann_ts_dt$ano))
 ann_ts_brks <- calc_sym_breaks(ann_ts_minval, ann_ts_maxval)

  # Title and y-axis label
 par_title <- if (parr %in% c("prcp", "soil_moisture")) {
   paste0(region,' ', parr_full, " (% of normal) 1950–", cur_yr)
 } else {
   paste0(region,' ', parr_full, " (", unt, ") 1950–", cur_yr)
 }

 y_axis_lab <- if (parr %in% c("prcp", "soil_moisture")) {
   paste0(parr_full, " anomaly (% of normal)")
 } else {
   paste0(parr_full, " anomaly (", unt, ")")
 }

 # plot
 ann_ano_ts_plt <- ggplot(ano_ann_ts_dt, aes(x = yr, y = ano)) +
   geom_bar(stat = "identity", aes(fill = ano), width = 0.7, show.legend = FALSE) +
   geom_smooth(method = "loess", color = "magenta", size = 1.2, se = FALSE) +
   geom_hline(yintercept = 0, color = "gray10", linewidth = 0.5) +

   scale_fill_gradientn(colours = cpt("ncl_BlWhRe", 100),
                        limits = c((-1* max(abs(c(ann_ts_minval, ann_ts_maxval)))),
                                   (1* max(abs(c(ann_ts_minval, ann_ts_maxval))))),
                        breaks = ann_ts_brks,
                        na.value = "transparent")+
   theme_ts_linear()+
   scale_x_continuous(
     name = " ",
     breaks = seq(1950, cur_yr, 2),
     expand = c(0.02, 0.02)
   ) +
   scale_y_continuous(name = y_axis_lab,
                      limits = c((-1* max(abs(c(ann_ts_minval, ann_ts_maxval)))),
                                 (1* max(abs(c(ann_ts_minval, ann_ts_maxval))))),
                      breaks = ann_ts_brks)
 labs(title = par_title)
 ann_ano_ts_plt

 if (parr %in% c("prcp", "soil_moisture"))  {
   ann_ano_ts_plt <- ann_ano_ts_plt +
     scale_fill_gradientn(
       name = paste0(parr, " anomaly ", unt),
       colours = cpt("cmocean_curl", 100, rev = TRUE),
       limits = c((-1* max(abs(c(ann_ts_minval, ann_ts_maxval)))),
                  (1* max(abs(c(ann_ts_minval, ann_ts_maxval))))),
       breaks = ann_ts_brks,
       na.value = "transparent")

 } else {
   ann_ano_ts_plt <- ann_ano_ts_plt
 }
 ann_ano_ts_plt

 ggsave(
   paste0(ann_summ_rslts_pth,parr,"_annual_ano_ts_plt_1950_", cur_yr,
          ".png"),
   plot =ann_ano_ts_plt,
   width = 16,
   height = 7.5,
   units = "in",
   dpi = 320,
   scale = 0.8,
   limitsize = F
 )

 ###  Final summary table ----------------------------------
 mon_summ_tbl%<>%
   mutate(type_prd = as.character(type_prd))

 ann_ano_sp_summ_tbl
 ann_sp_trn_summ_tbl
 ann_trn_summ_tbl

 fnl_summ_tbl <- bind_rows(mon_summ_tbl,
                           ann_ano_sp_summ_tbl,
                           ann_sp_trn_summ_tbl,
                           ann_trn_summ_tbl)
 fnl_summ_tbl



## Ranking table  ----------------------------------
ano_ann_ts_dt %>%
  mutate(ano_rank = rank(-rank(ano)))%>%
  dplyr::select(yr, rank = ano_rank, change = ano) %>%
  arrange(rank) %>%
  mutate(parr = parr) -> ann_ano_rnk_chng_tbl

write_csv(
  ann_ano_rnk_chng_tbl,
  paste0(
    ann_summ_rslts_pth,
    parr,
    '_bc_ann_ranking_change_table_', cur_yr,'.csv'
  )
)

## return final items list  -------------------------------------------------------------
  list(
    mon_ano_plt =  mon_ano_plt,
    ann_ano_plt  = yr_ann_sp_ano_plt,
    ann_ts_plt   = ann_ano_ts_plt,
    ann_ts_rnk_tbl    = ann_ano_rnk_chng_tbl,
    summ_tbl =  fnl_summ_tbl
  )
}

# Credit  -----
plt_wtrmrk <-
  "Created by Aseem Sharma (aseem.sharma@gov.bc.ca), BC Ministry of Forests. Data credit: ERA5land/C3S/ECMWF."
plt_wtrmrk

parameters

plan(sequential)

parrs_ann_summary_results_lst <- map(
  parameters,
  function(parr) {
    message("Processing: ", parr)
    ann_clm_summ_cal_plt_fun(
      ano_dt_fls  = ano_dt_fls,
      clm_dt_fls  = clm_dt_fls,
      bc_shp      = bc_shp,
      parr        = parr,
      cur_yr      = cur_yr,
      region = "BC"
    )
  }
) %>% set_names(parameters)

parrs_ann_summary_results_lst
# Access results for a specific parameter, e.g., "prcp"
parrs_ann_summary_results_lst[["prcp"]]$ann_ts_plt

parrs_ann_summary_results_lst

```

This report summarizes British Columbia (BC)'s climate conditions in `r cur_yr` based on three key variables: average temperature, total precipitation, and soil moisture derived from <a href='https://cds.climate.copernicus.eu/cdsapp#!/dataset/reanalysis-era5-land?tab=overview'>ERA5-Land hourly dataset</a>.

# Temperature in `r cur_yr`

```{r temp notes}
# Ordinal suffix helper (1st, 2nd, 3rd, 4th…)
ordinal_suffix <- function(n) {
  if (n %% 100 %in% c(11, 12, 13)) {
    paste0(n, "th")
  } else {
    paste0(
      n,
      c("th", "st", "nd", "rd", "th")[min(n %% 10 + 1, 5)]
    )
  }
}

tmp_summ_tbl <- parrs_ann_summary_results_lst$tmean$summ_tbl
tmp_summ_tbl

tmp_rnk_tbl <- parrs_ann_summary_results_lst$tmean$ann_ts_rnk_tbl
tmp_rnk_tbl

# Values
tmp_rank   <- tmp_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(rank)

tmp_change <- tmp_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(change)

# Direction wording (warm vs cool)
temp_direction <- if (tmp_change >= 0) "increased" else "decreased"
record_type    <- if (tmp_change >= 0) "warmest"  else "coolest"
```

In `r cur_yr`, the average annual temperature in British Columbia (BC) `r temp_direction` by `r round(abs(tmp_change), 2)`°C. This ranks as the `r ordinal_suffix(tmp_rank)` `r record_type` year on record since 1950 (@fig-bc_ann_temp_ano_ts). This warming trend reflects the ongoing global increase in surface temperatures; notably, 2025 ranked globally as the third warmest year since 1850, following only 2023 and 2024 ([Global Temperature Report 2025, Berkeley Earth](https://berkeleyearth.org/global-temperature-report-for-2025/)). In BC, 2023 remains the warmest year on record since 1950 with an average increase of 2.15°C. Highlighting the recent acceleration of climate change, seven of the ten warmest years in the province have occurred since 2010 (@tbl-bc_ann_temp_rank).

Spatially, annual average temperature in `r cur_yr` were above normal however with regional and seasonal variations.The Southern and Central Interior experienced the most significant warming (exceeding 2°C above historical baseline), while the northern coastal regions saw relatively smaller increases (@fig-bc_ann_ano_dist_plt).

The year was characterized by pronounced month-to-month temperature variability (@fig-bc_mon_temp_dist_plt).

-   **January:** Exceptionally mild conditions with warmer-than-normal temperature prevailed with a spatial mean temperature anomaly of **+2.75 °C** (range: −2.2 °C to +9.75 °C).

-   **February:** A sharp reversal to cooler-than-normal conditions occurred, with a spatial mean anomaly of **−3.54 °C** (range: −6.61 °C to +1.36 °C).

-   Above-normal temperatures persisted through most of the remaining months, with warming peaking in **September** and **November** .

-   **December:** A pronounced latitudinal contrast was observed; **northern BC** experienced significantly cooler-than-normal conditions, while **southern regions** remained exceptionally warm, producing a wide spatial anomaly range from **−11.6 °C to +6.71 °C** .

BC's average temperature rose by 2.40°C between 1950 and `r cur_yr` (and by 1.88°C (0.024 °C yr$^{-1}$) since 1980) based on ERA5-Land data. The province is currently warming at an average rate of **0.03**°C yr$^{-1}$ since 1950, with regional variations ranging from **0.01**°C yr$^{-1}$ to **0.06**°C yr$^{-1}$.

```{r temp-timeseries-anomaly-plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 7
#| fig-width: 12
#| label: fig-bc_ann_temp_ano_ts
#| fig-cap: !expr >
#|   paste0("Annual average air temperature anomalies for BC 1950–", cur_yr, 
#|   ". The bluish bars represent cooler-than-normal years, ",
#|   "while the reddish bars indicate warmer-than-normal years. ",
#|   "Anomalies are calculated relative to the 1981–2010 climatological baseline. ",
#|   "The magenta line represents the moving regression. Data credit: *ERA5land/C3S/ECMWF*.")

parrs_ann_summary_results_lst$tmean$ann_ts_plt +
  theme(
    plot.title   = element_text(size = rel(2)),   
    axis.title.x = element_text(size = rel(2)),
    axis.title.y = element_text(size = rel(1.5)),
    axis.text    = element_text(size = rel(2))
  )
```

```{r temp-ann-ano-dist-plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 8
#| fig-width: 13
#| label: fig-bc_ann_ano_dist_plt
#| fig-cap: !expr |
#|   paste0(
#|     "BC's average air temperature anomaly for ", cur_yr,
#|     " relative to the 1981–2010 reference period. ",
#|     "The bluish areas represent cooler-than-normal temperatures, ",
#|     "while the reddish areas indicate warmer-than-normal temperatures for ", cur_yr,
#|     ". Data credit: *ERA5land/C3S/ECMWF*."
#|   )

parrs_ann_summary_results_lst$tmean$ann_ano_plt +
  theme(
  plot.title = element_text(size = rel(1.0)))

```

```{r temp-ranking-table}
#| include: true
#| output: true
#| cache: false
#| tbl-cap-location: top
#| label: tbl-bc_ann_temp_rank
#| tbl-cap: !expr >
#|   paste0(
#|     "Mean air temperature change and ranking relative to the 1981–2010 average ",
#|     "for the top 15 warmest years between 1950 and ", cur_yr,
#|     " in BC. Data credit: *ERA5land/C3S/ECMWF*."
#|   )

tmp_rnk_tbl <- parrs_ann_summary_results_lst$tmean$ann_ts_rnk_tbl
tmp_rnk_tbl%<>%
  dplyr::select(-parr) %<>%
  slice(1:15)%<>%
   gt() %>%
  tab_header(
    title = "BC annual warming ranks"
  ) %>%
  rm_header()%>%
  fmt_number(
    columns = c(change),
    decimals = 2
  ) %>%
  cols_label(
    yr = "Year",
    rank = "Rank",
    change = "Warming (°C)"
  ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_column_labels(everything())
  ) %>%
  tab_options(
    table.font.size = 16,
    table.width = pct(50)
  )
tmp_rnk_tbl

```

```{r temp-mon-ano-dist-plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 12
#| fig-width: 16
#| label: fig-bc_mon_temp_dist_plt
#| fig-cap: !expr >
#|   paste0(
#|     "Monthly average air temperature anomalies for BC in ", cur_yr,
#|     ". The bluish areas represent months with cooler-than-normal temperatures, ",
#|     "while the reddish areas indicate months with warmer-than-normal temperatures. ",
#|     "Data credit: *ERA5land/C3S/ECMWF*."
#|   )

 parrs_ann_summary_results_lst$tmean$mon_ano_plt +  theme(
  plot.title = element_text(size = rel(2))
)

```

# Precipitation in `r cur_yr`

```{r prcp notes}
prcp_summ_tbl <- parrs_ann_summary_results_lst$prcp$summ_tbl
prcp_summ_tbl

prcp_rnk_tbl <- parrs_ann_summary_results_lst$prcp$ann_ts_rnk_tbl
prcp_rnk_tbl
parrs_ann_summary_results_lst$prcp$ann_ano_plt
parrs_ann_summary_results_lst$prcp$ann_ts_plt
parrs_ann_summary_results_lst$prcp$mon_ano_plt

# Values
prcp_rank   <- prcp_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(rank)

prcp_change <- prcp_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(change)
prcp_change

# Direction wording (warm vs cool)
prcp_direction <- if (prcp_change >= 0) "higher" else "lower"
prcp_record_type    <- if (prcp_change >= 0) "wetter"  else "drier"
```

On average, total annual precipitation in BC during `r cur_yr` was slightly `r prcp_direction` by `r round(abs(prcp_change), 2)`% of the 1981–2010 historical average. Based on ERA5-Land data, this marks a continued decline in total annual precipitation observed since 2022 (@fig-bc_ann_prcp_ano_ts).

However, the province exhibited considerable spatial variability (@fig-bc_ann_ano_prcp_dist_plt). **Vancouver Island**, the **Lower Mainland**, the **Interior Plateau**, and **Northeast BC** experienced below-normal precipitation, with parts of the Northeast receiving over 25% less than the historical average. Conversely, the mountainous **Kootenay region** and the **central-to-northern coastal regions** recorded higher-than-normal precipitation. Atmospheric River (AR) events played a substantial role in delivering these large moisture volumes to the province.

The monthly distribution of precipitation anomaly (@fig-bc_mon_prcp_dist_plt) highlights the following key variations:

-   **Winter Deficits:** The year began with a significantly drier **January** (26% below normal) and **February** (25% below normal) across the majority of the province.
-   **Latitudinal Contrast in March:** March experienced split conditions; lower latitudes saw wetter-than-average weather (over 100% above normal), while northern latitudes remained dry, recording deficits of up to 56%.
-   **Regional Spring Divergence (April–May):** While April was generally drier than normal, **May** brought a significant shift. The **Northwest Coast** became exceptionally wet (over 100% above normal), with near-record rainfall driven by persistent low-pressure systems. In contrast, the **Northeast and Kootenay regions** experienced intensified drying.
-   **Summer Transitions and August AR:** Summer began with a dry **June**, followed by variable conditions in July and August. A rare **summer atmospheric river (August 15–17)** delivered significant moisture to the South Coast, pushing monthly totals above normal.
-   **September** was substantially drier than average for most of the province. However, strong atmospheric rivers delivered heavy precipitation concentrated along the **Coastal and South Coast regions** making the region wetter than normal.
-   **December:** The year concluded with a very wet **December** (over 85% above normal), the result of a sequence of back-to-back atmospheric rivers making landfall.

```{r prcp timeseries anomaly plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 7
#| fig-width: 12
#| label: fig-bc_ann_prcp_ano_ts
#| fig-cap: !expr >
#|   paste0("Annual total precipitation anomalies (% of normal) for BC 1950–", cur_yr, 
#|   ". greenish bars represent wetter-than-normal years, ",
#|   "while the brownish bars indicate drier-than-normal years. ",
#|   "Anomalies are calculated relative to the 1981–2010 climatological baseline. ",
#|   "The magenta line represents the moving regression. Data credit: *ERA5land/C3S/ECMWF*.")

parrs_ann_summary_results_lst$prcp$ann_ts_plt +
  theme(
  plot.title = element_text(size = rel(2)),   
  axis.title.x = element_text(size = rel(2)),
  axis.title.y = element_text(size = rel(1.5)),
  axis.text = element_text(size = rel(2))
)

```

```{r prcp ann ano dist plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 8
#| fig-width: 13
#| label: fig-bc_ann_ano_prcp_dist_plt
#| fig-cap: !expr |
#|   paste0(
#|     "BC's annual average precipitation anomaly for ", cur_yr,
#|     " relative to the 1981–2010 reference period. ",
#|     "The greenish areas represent wetter-than-normal precipitation areas, ",
#|     "while the brownish areas indicate drier-than-normal precipitation for ", cur_yr,
#|     "Data credit: *ERA5land/C3S/ECMWF*"
#|   )

parrs_ann_summary_results_lst$prcp$ann_ano_plt +
  theme(
  plot.title = element_text(size = rel(1.0)))

```

```{r prcp mon ano dist plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 12
#| fig-width: 16
#| label: fig-bc_mon_prcp_dist_plt
#| fig-cap: !expr >
#|   paste0(
#|     "Monthly average total precipitation anomalies ( % of normal) for BC in ", cur_yr,
#|     ". The greenish areas represent wetter-than-normal precipitation areas, ",
#|     "while the brownish areas indicate drier-than-normal precipitation regions. ",
#|     "Data credit: *ERA5land/C3S/ECMWF*."
#|   )

 parrs_ann_summary_results_lst$prcp$mon_ano_plt +  theme(
  plot.title = element_text(size = rel(2))
)

```

# Soil moisture in `r cur_yr`

```{r soil mositure notes}
sm_summ_tbl <- parrs_ann_summary_results_lst$soil_moisture$summ_tbl
sm_summ_tbl

sm_rnk_tbl <- parrs_ann_summary_results_lst$soil_moisture$ann_ts_rnk_tbl
sm_rnk_tbl
parrs_ann_summary_results_lst$soil_moisture$ann_ano_plt
parrs_ann_summary_results_lst$soil_moisture$ann_ts_plt
parrs_ann_summary_results_lst$soil_moisture$mon_ano_plt

# Values
sm_rank   <- sm_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(rank)

sm_change <- sm_rnk_tbl %>%
  filter(yr == cur_yr) %>%
  pull(change)
sm_change

# Direction wording (warm vs cool)
sm_direction <- if (sm_change >= 0) "higher" else "lower"
sm_record_type    <- if (sm_change >= 0) "wetter"  else "drier"
```

Volumetric soil moisture is an important indicator of water availability for plant uptake, groundwater recharge, drought, and other hydrological processes. The average annual volumetric soil moisture (0 - 1 m) in BC in `r cur_yr` was `r sm_direction` by `r round(abs(sm_change), 2)`% of the 1981–2010 historical average (@fig-bc_ann_soil_ano_ts). While this represents a slight recovery from the record-breaking dry conditions of 2023, the province remains in a significant long-term drying trend, with average soil moisture content decreasing by 3.04% since 1980 (a rate of 0.042% per year).

While the provincial average shows a moderate deficit, spatial variability of soil mositure across the region is stark (@fig-bc_ann_ano_soil_dist_plt):

-   Northeast BC & Peace Region: This area remained the epicenter of the drought, with soil moisture levels persisting at over 20% below normal throughout the entire year. This represents a multi-year continuation of extreme moisture deficits (2024 report).

-   Southern Interior & Coast: These regions also saw substantial deficits on the annual average soil mositure particularly in the southwest.

-   Northwest BC: Conversely, the Northwest experience soil moisture levels 5–15% above normal in `r cur_yr`.

A monthly variations exists throughout `r cur_yr` in soil mositure content; while some months provided temporary relief, others exacerbated the drought conditions (@fig-bc_mon_soil_dist_plt).

-   **The Driest Months**: **September** was the driest month of the year, followed closely by **June** and **July**. During September, nearly the entire province (with the exception of the far northwest) showed moderate to severe moisture deficits.

-   The **spring months** (notably April), along with **August** and **December**, observed slightly higher-than-normal soil moisture on average.

-   Regardless of the season, the **Northeast** remained drier than normal for all twelve months of 2025, highlighting a chronic lack of moisture recharge and proglong drought in that region.

```{r soil moisture timeseries anomaly plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 7
#| fig-width: 12
#| label: fig-bc_ann_soil_ano_ts
#| fig-cap: !expr >
#|   paste0("Annual average volumetirc soil moisture (0-1 m) anomalies (% of normal) for BC 1950–", cur_yr, 
#|   ". greenish bars indicate wetter-than-normal years, ",
#|   "while the brownish bars indicate drier-than-normal years. ",
#|   "Anomalies are calculated relative to the 1981–2010 climatological baseline. ",
#|   "The magenta line represents the moving regression. Data credit: *ERA5land/C3S/ECMWF*.")

parrs_ann_summary_results_lst$soil_moisture$ann_ts_plt +
  theme(
  plot.title = element_text(size = rel(2)),   
  axis.title.x = element_text(size = rel(2)),
  axis.title.y = element_text(size = rel(1.5)),
  axis.text = element_text(size = rel(2))
)

```

```{r soil moisture ann ano dist plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 8
#| fig-width: 13
#| label: fig-bc_ann_ano_soil_dist_plt
#| fig-cap: !expr |
#|   paste0(
#|     "BC's annual average soil moisture anomaly for ", cur_yr,
#|     " relative to the 1981–2010 reference period. ",
#|     "The greenish areas represent wetter-than-normal soil moisture areas, ",
#|     "while the brownish areas indicate drier-than-normal soil moisture areas for ", cur_yr,
#|     ".Data credit: *ERA5land/C3S/ECMWF*"
#|   )

parrs_ann_summary_results_lst$soil_moisture$ann_ano_plt +
  theme(
  plot.title = element_text(size = rel(1.0)))

```

```{r soil mon ano dist plt}
#| include: true
#| output: true
#| cache: false
#| fig-align: left
#| fig-height: 12
#| fig-width: 16
#| label: fig-bc_mon_soil_dist_plt
#| fig-cap: !expr >
#|   paste0(
#|     "Monthly average volumertirc soil moisture anomalies ( % of normal) for BC in ", cur_yr,
#|     ". The greenish areas represent wetter-than-normal areas, ",
#|     "while the brownish areas indicate drier-than-normal soil moisture regions. ",
#|     "Data credit: *ERA5land/C3S/ECMWF*."
#|   )

 parrs_ann_summary_results_lst$soil_moisture$mon_ano_plt +  theme(
  plot.title = element_text(size = rel(2))
)

```

This report is a companion to the <a href="https://bcgov-env.shinyapps.io/bc_climate_anomaly/">BC Climate Anomaly App</a>. For regional breakdowns, detailed trends, and underlying data, please refer to the app.

<p style="font-size:0.6em; line-height:1.3;">

<strong>Disclaimer</strong><br> This report is prepared using <a href='https://www.ecmwf.int/en/era5-land'>ERA5-Land</a> data from the European Centre for Medium-Range Weather Forecasts (ECMWF), as available at the time of preparation. The original data may be subject to updates or revisions.Any modifications to the original data may result in adjustments to the findings presented in this report.

</p>

```{r file copy to www folder for app}
file.copy(from = paste0('bc_annual_climate_summary_',cur_yr,'.html'), to = "../www/", overwrite = T)
```
